iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-28 manuscript/main.tex
stub of author contribution

\subsection*{Author contributions}
In order to give appropriate credit to each author of an article, the individual
contributions of each author to the manuscript should be detailed in this section. We
recommend using author initials and then stating briefly how they contributed.

>>>>

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
All authors wrote and approved the final manuscript.
